Secure Composition of Robust and Optimising Compilers

### 2023-06-24 popl/main.tex
Parts of Relwork

\section{Introduction}

@@

\section{Background}\label{sec:background}
\Cref{subsec:bg:tprop} introduces trace properties, monitors, and property satisfaction.
\Cref{subsec:bg:rtp} extends the property satisfaction with robustness and shows its compiler-driven preservation, as presented in~\cite{abate2019jour}.

@@

\section{Composing Properties}\label{sec:compprop}
\Cref{subsec:propdefs} introduces a ,,most general'' trace model and defines properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{cct}) that the case study (\Cref{sec:casestud}) uses.
By means of taking these properties as an example, \Cref{subsec:monitors} defines monitors for them and an agreement relation between a monitor's trace model with the most general trace model.
Then, monitor-based satisfaction is introduced and it is proven that trace-property satisfaction is implied by it.
Since monitor-based satisfaction is easier to reason about, this simplifies later proofs considerably.

@@

\section{Composing Secure Compilers}\label{sec:compcomp}

@@

%\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
\section{Case Study: Preliminary Definitions}\label{sec:casestud:defs}

@@

\section{Case Study: Secure Compiler Compositions in the Wild}\label{sec:casestud:rtp}

@@

\section{Related Work}\label{sec:relwork}

@@

The robust preservation of properties as a compiler--level criterion has been analyzed extensively~\cite{abate2019jour,patrignani2021rsc,abate2021extacc,patrignani2022universal,patrignani2019survey,kruse2022csc}.
This work has made use of that previous work and formalized the compositionality aspect which has not been explored before.
While there exists a composition theorem~\cite{abate2019jour} already, that theorem is not concerned with composing robustly safe compilers, but rather program components and contexts.
The work relating robust preservation with universal composability~\cite{patrignani2022universal} is closest to what this paper presents.
The authors demonstrate a similar compositionality theorem to what is presented here (\Cref{sec:compcomp}).
However, they do not demonstrate the scalability of the approach in the context of a practical compilation chain.

@@

\cite{michael2023mswasm}

@@

\section{Conclusion}\label{sec:concl}

>>>>

\section{Introduction\pages{4}}

@@

\section{Background\pages{1}}\label{sec:background}
\Cref{subsec:bg:tprop} introduces trace properties, monitors, and property satisfaction.
\Cref{subsec:bg:rtp} extends the property satisfaction with robustness and shows its compiler-driven preservation, as presented in~\cite{abate2019jour}.

@@

\section{Composing Properties\pages{3}}\label{sec:compprop}
\Cref{subsec:propdefs} introduces a ,,most general'' trace model and defines properties (\gls{tms}, \gls{sms}, \gls{ms}, and \gls{cct}) that the case study (\Cref{sec:casestud}) uses.
By means of taking these properties as an example, \Cref{subsec:monitors} defines monitors for them and an agreement relation between a monitor's trace model with the most general trace model.
Then, monitor-based satisfaction is introduced and it is proven that trace-property satisfaction is implied by it.
Since monitor-based satisfaction is easier to reason about, this simplifies later proofs considerably.

@@

\section{Composing Secure Compilers\pages{1\sfrac{1}{2}}}\label{sec:compcomp}

@@

%\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
\section{Case Study: Preliminary Definitions\pages{6}}\label{sec:casestud:defs}

@@

\section{Case Study: Secure Compiler Compositions in the Wild\pages{7}}\label{sec:casestud:rtp}

@@

\section{Related Work\pages{2}}\label{sec:relwork}

@@

The robust preservation of properties as a compiler--level criterion has been analyzed extensively~\cite{abate2019jour,patrignani2021rsc,abate2021extacc,patrignani2022universal,patrignani2019survey,kruse2022csc}.
This work has made use of that previous work.
While there exists a composition theorem~\cite{abate2019jour} already, that theorem is not concerned with composing robustly safe compilers, but rather program components and contexts.
The work relating robust preservation with universal composability~\cite{patrignani2022universal} is closest to what this paper presents.
The authors demonstrate a similar compositionality theorem to what is presented here (\Cref{sec:compcomp}) as well as in an earlier version of this work~\cite{kruse2022csc}.
However, they do not demonstrate the scalability of the approach in the context of a compilation chain.

@@

There is still no consensus what the formal definition of memory safety as a program property should be. %cite
Yet, different mechanisms for memory safety exist that also consider the secure compilation domain, i.e., have an attacker model that is not just the observing attacker.
For example, the ,,pointers as capabilities'' principle represents pointers as machine--level capabilities~\cite{korashy2021capableptrs}, which behave in a similar fashion to capabilities by means of  linear typing~\cite{morrisett2005L3}.
The approach of this paper to memory safety and the countermeasures against memory safety insecurities are inspired by seminal work in the literature~\cite{nagarakatte2009soft,nagarakatte2010cets}.
The view of memory safety in this paper exhibits the classic split between temporal and spatial memory safety.
The former making sure that there are no double deallocations or use after frees.
The latter making sure that there are no out of bounds accesses.
When extending the languages in this paper with a less restricted form of pointer arithmetic, the region coloring memory safety monitor presented in earlier work~\cite{michael2023mswasm} can be used.
The work presenting this monitor provides an approach for the robust {\em enforcement}, which implies robust preservation, of memory safety.
But, they do not compose the enforcement mechanism with other secure compilation passes.

@@

\section{Conclusion\pages{$\sfrac{1}{2}$}}\label{sec:concl}
